---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ggcalheatmap

The goal of ggcalheatmap is to plot a calendar heatmap with a `ggplot2` backend.
I found recently that [`ggTimeSeries`](https://github.com/AtherEnergy/ggTimeSeries) as the same functionnality with its
function `ggplot_calendar_heatmap`. There should not be lot of differences between the two packages but the default parameters.
Also, by default, `ggcalheatmap` can produce interactive calendar heatmaps.

## Installation

You can install ggcalheatmap with:

```{r install, eval=FALSE}
remotes::install_github("denrou/ggcalheatmap")
```

## Example

This is a basic example where we want to look at all contributions stored in all of our git repositories stored in `HOME`:

```{r example_install, eval=FALSE}
remotes::install_github("denrou/ggit")
# Yes this is an auto-promotion :)
```

```{r contribution}
df <- ggit::contributions(path = Sys.getenv("HOME"))
df
```

```{r calendar_heatmap}
ggcalheatmap::ggcalheatmap(df[lubridate::year(df[["when"]]) >= 2017, ], "when", "n", tooltip = FALSE)
```

The `tooltip` parameter, if TRUE, creates an interactive plot that can be placed in any rmarkdown document. It uses [`ggiraph`](https://davidgohel.github.io/ggiraph/articles/offcran/using_ggiraph.html)
